---
title: "Initial Statistical Inference on 40 Exponents"
author: "Danish Tamboli"
date: "8/5/2020"
output: pdf_document
---

# Initial Statistical Inference on 40 Exponents, and comparison with CLT Distribution.

## Overview:
 * Comparison between Exponential Distribution and Central Limit Theorem Distribution (Normal Distribution) of 40.

### What does Central Limit Theorem state?
 * The central limit theorem states that if you have a population with :
   * mean mu.
   * standard deviation sigma.
   * Take sufficiently large random samples from the population with replacement.
   * The distribution of the sample means will be approximately normally distributed.
   * Here we are assuming lambda = 0.2, mu = 1\/lambda and sigma = 1\/lambda.
   * Here we will be taking 1000 simulations or sample sets from the 40 exponents.
   
### Simulation:
```{r, Expontent and clt Distribution}

set.seed(103101)
init_exp <- rexp(40,0.2)
exp_mean <- mean(init_exp)
print(paste("Observed Exponent Mean:", exp_mean))

clt <- sapply(1:1000, function(i){mean(sample(init_exp,replace = TRUE))})
clt_mean <- mean(clt)
print(paste("Observed Cental Limit Theorem Mean:", clt_mean))
```
### Sample Mean versus Theoretical Mean:

 * From the above we can discuss the Theoretical and Observed means:

   * We see that as lambda is 0.2, Hence the Theoretical mean = 1\/lambda should be 5
   * The Observed Exponent Mean and Observed Central Limit Theorem Mean is \~ the Theoretical mean. 

```{r}

variance_exp <- var(init_exp)
print(paste("Observed Exponent Variance:",variance_exp))

variance_clt <- var(clt)
print(paste("Observed Cental Limit Theorem Variance:",variance_clt))

```
### Sample Variance versus Theoretical Variance: 

 * From the above we can discuss the Theoretical and Observed variances:

   * We see that as lambda is 0.2, Hence the Theoretical variance = sd^2, sd = (1/lambda) = 5 should be 25
   * The Observed Exponent Variance is \~ the Theoretical mean.
 
### Distribution:
```{r, Distribution Graphs,fig.height=4,echo=FALSE}
library(ggplot2)
plot <- ggplot(data=as.data.frame(init_exp),aes(init_exp)) + geom_histogram(aes(init_exp, y = ..density..),color="white",fill="grey",bins = 30) + labs(x= "Density", y= "Exponent Value",title = "Distibution of 40 Exponents") + geom_vline(xintercept=5,lwd=2,col="blue") + geom_vline(xintercept = mean(init_exp),lwd=2)
plot

x <- seq(min(clt),max(clt),length=1000)
plot1 <- ggplot(data= as.data.frame(clt),aes(clt)) + geom_histogram(aes(clt,y =..density..),color="white",fill="grey",bins = 30) + geom_line(aes(x,dnorm(x,mean(clt),sd(clt))),color="yellow",lwd=2) + labs(x = "Exponent Value", y = "Density",title = "Distribution of 1000 averages of mean of 40 Exponents") + geom_vline(xintercept=5,lwd=2,col="blue") + geom_vline(xintercept = clt_mean,lwd=2)
plot1
```

 
 * From the above 2 figures we can see how the Central Limit Distribution (grey bars) is approximately normal (yellow line), as how it fits under the curve of the normal line (yellow).
 
```{r,qqplots,fig.height=4,echo=FALSE}

qqnorm(init_exp,main = "QQPlot of 40 Exponents",col="orange")
qqline(init_exp,col="green")

qqnorm(clt,col=c("orange",alpha=0.95))
qqline(clt,main = "QQPlot of CLT Normal Distribution",col="green")

```
 
  * From the above 2 figures we can clearly see:
    * How the 40 exponents is not normal and hence the points are not on the straight line.
    * How the CLT Distribution is of Normal Distribution Type as majority of the points are on the straight line.
 
 